%------------------------
% Resume
% Author : Adam Mischke
% Github : https://github.com/vanities
% License : MIT
%------------------------

\documentclass[a4paper,20pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{tabularx}
\usepackage[dvipsnames]{xcolor}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.45in}
\addtolength{\textheight}{1in}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemWithoutTitle}[1]{
  \item\small{
    {\vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-3pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-----------------------------
%%%%%%  CV STARTS HERE  %%%%%%

\begin{document}

%----------HEADING-----------------
%  & Email: \href{mailto:}{mischke@protonmail.com}
\begin{tabularx}{\textwidth}{X|X|X|X}
  \href{https://catwebm.com}{catwebm.com}
  ~~~+1-931-998-0046
  \textbf{{\LARGE Adam Mischke}}
  \href{mailto:}{mischke@protonmail.com}
  \href{https://github.com/vanities}{~~github.com/vanities}
\end{tabularx}

%----------SUMMARY-----------------
{\color{BrickRed} \section{Summary}}
  Strong work ethic Full-stack Engineer that learns quickly and is a committed team player. Has 4-years of startup experience working in an agile and TDD environment. Served in the United States Navy as a Network Administrator.
 \vspace{12pt}

%-----------EDUCATION-----------------
{\color{YellowOrange} \section{Education}}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Middle Tennessee State University}{Murfreesboro, Tennessee}
      {Bachelor of Science - Computer Science; Minor in Mathematics}{July 2014 - June 2018}
      {\scriptsize \textit{ \footnotesize{\newline{}\textbf{Awards / Memberships:} Dean’s List 2014-2018, Member of Association of Computing Machinery (ACM), Member of the Upsilon Pi Epsilon Computer Honor Society}}}
    \resumeSubHeadingListEnd
\vspace{-5pt}

%----------SKILLS-----------------
{\color{Mulberry} \section{Skills}}
	\resumeSubHeadingListStart
	\resumeSubItem{Languages}{~~~~~~Python, Swift, JavaScript, C++, SQL, Bash, Solidity }
	\resumeSubItem{Frameworks}{~~~~Django, Flask, NodeJS, React, SwiftUI }
	\resumeSubItem{Tools}{~~~~~~~~~~~~~~Docker, Terraform, GIT, PostgreSQL, Fastlane}
	\resumeSubItem{Platforms}{~~~~~~~Mac, Linux, Web, iOS, AWS, GCP, Firebase, Github, Datadog, Sentry, Code Climate, CircleCI}
	\resumeSubItem{Soft Skills}{~~~~~~~Leadership, Problem Solving, Strong Communication Skills, Time Management}
\resumeSubHeadingListEnd
\vspace{-5pt}

%----------EXPERIENCE-----------------
{\color{ForestGreen} \section{Experience}}
  %----------FUN-----------------
  \resumeSubHeadingListStart
    \resumeSubheading{FunFunFun Inc. - Gen Z Dating}{Remote}
    {Full-stack Engineer (Full-time)}{May 2020 - June 2022}
    \resumeItemListStart
        \resumeItem{First Engineering Hire}
          {Created a live updating video dating app that integrated with TikTok with over 10,000 users, where users could like, match, and message each-other.}
          \resumeItem{Backend}
          {Built a Django and GraphQL and a matching algorithm to pair users together with alike parameters.}
          \resumeItem{Frontend}
          {Deployed a complete SwiftUI app from the ground up to app store. Contributed to an internal Typescript React webpage to police uploaded media and content used by admins.}
          \resumeItem{DevOps}
          {Used GitHub actions to create an CI/CD pipeline for the backend and iOS using fastlane for multiple environments.}
          \resumeItem{Algorithms}
          {Created a series of Firebase, Firestore, and Google Storage Typescript triggers to create a video processing pipeline that asynchronously cut over 8,000 videos.}
      \resumeItemListEnd
\vspace{-5pt}

    %----------COINMINE-----------------
    \resumeSubheading
		{Coinmine - Crypto Mining Made Easy}{Remote}
		{Software Engineer (Full-time - Part-time)}{May 2018 - Current}
		\resumeItemListStart
        \resumeItem{First Engineering Hire}
        {Built and maintained mineOS, an Arch Linux-Based Operating System, onto a small form factor computer that mined 6 different cryptocurrencies 24/7 that users could plug and play at home.}
        \resumeItem{mineOS}
        {Fabricated the build and deployment tools for distributing mineOS images through a test and build pipeline for over 5,000 miners.}
        \resumeItem{Backend}
        {Used Agile, Extreme Programming and Test Driven Development methodologies to deploy, update, and configure a Django based backend with over 8,000 users.}
        \resumeItem{DevOps}
        {Arranged and operated analytical, deployment, and pipeline tools such as: CircleCI, Code Climate, Datadog, and Sentry.}
        \resumeItem{Frontend}
        {Collaborated with React Native Engineer to build smooth frontend experience between API and Coinmine machine.}
        \resumeItem{Leadership}
        {Worked with overseas distribution centers to construct and create Standard Operating Procedures (SOP) for assembly and manufacturing.}
		\resumeItemListEnd
\vspace{-5pt}

    %----------CAT-----------------
    \resumeSubheading
		{Caterpillar Financial Services Corporation}{}
		{Information Services - Network Team (Intern)}{May 2017 – July 2017}
		\resumeItemListStart
        \resumeItem{Leadership}
        {Led research, meetings, and recommended the replacement of a network team application. Worked as liaison between team members and company solutions. Then sought out quote to be implemented into the yearly budget.}
        \resumeItem{Problem Solving}
        {Researched and developed a web dashboard that displayed global network information with Python and Flask using a SQL database. Used JavaScript, J-Query, Bootstrap, AJAX, and Google Charts to form a coherent and simple-to-use website. Implemented a search function that integrated with database calls to speed up information flow.}
		\resumeItemListEnd
\vspace{-5pt}

 %----------NAVY-----------------
    \resumeSubheading
		{United States Navy}{}
		{Fire controlman (FC2) - Computer and Network Technician (Full-time)}{July 2008 - July 2014}
		\resumeItemListStart
        \resumeItem{Leadership}
        {Efficiently led as work center supervisor, 8 personnel in accomplishing over 1,634 maintenance actions with a 94\% maintenance accomplishment rate, managing 372 maintenance checks and repairs.}
        \resumeItem{Security Clearance}
        {Held a Secret Clearance and handled the Electronic Key Management System, which managed 106 classified software programs and hardware systems.}
        \resumeItem{Preventative \& Corrective Maintenance}
        {Upkeep and corrective maintenance of the Ship's Self Defense System, Open architecture network server and computer systems, Battle Force Tactical Trainer network, and Cooperative Engagement Capability LAN.}
        \resumeItem{Teamwork}
        {Assisted in the successful overhaul of 3 major system installs with lead engineers to include: Hardware, software, and network installation, troubleshooting to the perfection of the system.}
		\resumeItemListEnd
\vspace{-5pt}
\resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\vspace{-5pt}
\section{Projects}
\resumeSubHeadingListStart
\resumeSubItem{Vison - multimedia search engine (NLP, Search Engine, Web Crawlers, Multimedia Processing)}{(Work in progress) Research oriented, open source, search engine for bringing reverse multimedia search to small \& mid scale enterprises. Tech: Python, NodeJS, Intel OpenVino Toolkit, Selenium, TensorFlow (October '18)}
\vspace{2pt}
\resumeSubItem{Reinforcement Learning based Traffic Control System (Reinforcement Learning, Computer Vision)}{AI model to resolve city traffic around 50\%
faster. Tech: Python, Alibaba Cloud, Raspberry Pi, Arduino, SUMO \& OpenCV. (August '18)}
\vspace{2pt}
\resumeSubItem{Panorama from Satellite Imagery using Distributed Computing (Distributed Computing, Image Processing)}{Images clicked using drones, provided by ISRO were stitched together using distributed public compute nodes, effectively bringing down processing time exponentially. Tech: PHP, C++, Java, Python (March '18)}
\vspace{2pt}
\resumeSubItem{Drag-n-drop machine learning learning environment (Web Development, Machine Learning)}{Scratch like tool for implementing machine learning pipelines along with built in tutorial for each concept. Tech: Python, JavaScript (September '18)}
\vspace{2pt}
\resumeSubItem{Search Engine and Social Network(Web Development, Web Crawler, Search)}{Created from scratch a social network and a search engine based on the idea of integrating Facebook and Google. The launched website was among top 1000 websites in India during 2012-2013. Tech: PHP, MySQL, HTML, CSS, WebSockets, JavaScript, RSS, XML ( May '12)}
\resumeSubHeadingListEnd
\vspace{-5pt}
\end{document}
